Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-11-25 rnni_convexity.tex
abstract pass

\begin{abstract}
Within this paper we consider a graph of ranked trees, that are rooted binary phylogenetic trees where internal nodes are ordered.
The ranking of these internal nodes can be seen as a discretisation of trees where internal nodes are assigned divergence times.
For phylogenetic reconstruction such as Markov Chain Monte Carlo (MCMC) methods, it is important to understand the geometry of tree spaces.
This motivates our work, which focusses on understanding the geometry of the space of ranked trees, the so-called ranked nearest neighbour interchange ($\rnni$) graph.
Moreover, we are interested in understanding the complexity of computing distances in this graph.
We will see that even though there are similarities between the $\rnni$ graph on ranked trees and the classical nearest neighbour interchange ($\nni$) graph on unranked phylogenetic trees, some significant differences between these tree spaces suggest that there is a difference in the complexity of computing distances.
\end{abstract}

>>>>

\begin{abstract}
In this paper we study the graph of ranked phylogenetic trees where the adjacency relation is given by a local rearrangement of the tree structure.
Our work is motivated by tree inference algorithms, such as maximum likelihood and Markov Chain Monte Carlo methods, where the geometry of the search space plays a central role for efficiency and practicality of the optimisation.
We hence focus on understanding the geometry of the space (graph) of ranked trees, the so-called ranked nearest neighbour interchange ($\rnni$) graph.
\todo{Geometry summary}
Specifically, we...

We also study the problem of computing distances between trees in this graph.
Since the $\rnni$ graph is a generalisation of the classical nearest neighbour interchange ($\nni$) graph to ranked phylogenetic trees, we specifically focus on the properties that have already been established for $\nni$.
Surprisingly, our results suggest that the complexity of computing distances in the two graphs is likely to be different.
\todo{Algorithms summary}
Specifically, we...
\end{abstract}
